Land doesn't get cancer, people do: an experiment comparing the effectiveness of two displays

### 2020-01-02 paper/paper.Rmd
title change

---
title: "Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison using visual inference"
affiliation:
  author-columnar: true         ## one column per author
  #institution-columnar: true  ## one column per institution (multiple autors eventually)
  # wide: true                  ## one column wide author/affiliation fields
  institution:
    - name: Queensland University of Technology
      department: Science and Engineering Faculty
      location: Brisbane, Australia
      email: stephanie.kobakian@qut.edu.au
      mark: 1
      author:
        - name: Stephanie Kobakian
    - name: Monash University
      department: Econometrics and Business Statistics Faculty
      location: Melbourne, Australia
      email: dicook@monash.edu
      mark: 1
      author:
        - name: Dianne Cook
keywords: ["statistics", "visual inference", "geospatial", "population"]
abstract: |
  The abstract goes here.
  On multiple lines eventually.
dev: png
bibliography: mybibfile.bib
output: rticles::ieee_article
editor_options: 
  chunk_output_type: inline
link-citations: yes
---

>>>>

---
title: "Land doesn't get cancer, people do: an experiment comparing the effectiveness of two displays"
affiliation:
  author-columnar: true         ## one column per author
  #institution-columnar: true  ## one column per institution (multiple autors eventually)
  # wide: true                  ## one column wide author/affiliation fields
  institution:
    - name: Queensland University of Technology
      department: Science and Engineering Faculty
      location: Brisbane, Australia
      email: stephanie.kobakian@qut.edu.au
      mark: 1
      author:
        - name: Stephanie Kobakian
    - name: Monash University
      department: Econometrics and Business Statistics Faculty
      location: Melbourne, Australia
      email: dicook@monash.edu
      mark: 1
      author:
        - name: Dianne Cook
keywords: ["statistics", "visual inference", "geospatial", "population"]
abstract: |
  The abstract goes here.
  On multiple lines eventually.
dev: png
bibliography: mybibfile.bib
output: rticles::ieee_article
editor_options: 
  chunk_output_type: inline
link-citations: yes
---

### 2020-01-02 paper/paper.tex
title change

\hypersetup{
            pdftitle={Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison using visual inference},
            pdfkeywords={statistics, visual inference, geospatial, population},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Which is Better: a Choropleth Map or Hexagon Tile Map? A comparison
using visual inference}

>>>>

\hypersetup{
            pdftitle={Land doesn't get cancer, people do: an experiment comparing the effectiveness of two displays},
            pdfkeywords={statistics, visual inference, geospatial, population},
            pdfborder={0 0 0},
            breaklinks=true}
\urlstyle{same}  % don't use monospace font for urls

@@

\begin{document}
%
% paper title
% Titles are generally capitalized except for words such as a, an, and, as,
% at, but, by, for, in, nor, of, on, or, the, to and up, which are usually
% not capitalized unless they are the first or last word of the title.
% Linebreaks \\ can be used within to get better formatting as desired.
% Do not put math or special symbols in the title.
\title{Land doesn't get cancer, people do: an experiment comparing the
effectiveness of two displays}
